Modeling the Evolution of Mimicry

### 2016-02-25 docs/paper/Paper.tex
Updates to the inspiration section

\subsubsection{Definitions of Mimicry}
The following account on the definition of Mimicry is mostly extracted from Wickler's \textit{Mimicry in plants and animals} \cite{wickler1986}.

According to Wickler the definition of mimicry provided by Bates \cite{bates1862} is quite restricted and is similar to the following

\begin{quote}
\textsl{``resemblance in external appearance, shapes and colors between members of widely distinct families."}
\end{quote}

The following more sophisticated definition was provided at the international Zoological Congress in Washington, 1963,

\begin{quote}
\textsl{``Mimicry is the close resemblance of one organism to another which, because it is unpalatable and conspicuous, is recognized and avoided by some predators at some times."}
\end{quote}

The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}. The clauses are presented in the following:

\begin{itemize}
	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".} This increases the probability that a predator will affect both parties concerned. Nevertheless, the model could live in Africa and the mimic in Europe, or vice versa, if the deceptive predator were a migratory bird.
	\item \textsl{``that the imitators are always the more defenseless".} On the contrary, for the case of Mertensian mimicry among coral snakes the more offensive party may occasionally be the mimic.
	\item \textsl{``that the imitators are always less numerous in individuals".} What is meant here is that the deceived animal should encounter the mimic less often than the model. This is true when the deceived animal must learn to recognize model and mimic and when positive and negative experiences carry equal weight. But it is known from various learning experiments that when an animal has learned about warning coloration, negative experiences or punishment stimuli (such as inedibility) can have a stronger and more lasting effect than positive experiences. Accordingly it should be expected that there would be an excess of mimics over models in proportion to the degree of predominance of negative experiences over positive onces. When the deceptive animal possesses an innate reaction to the model, the number of mimics can be virtually unlimited. 
	\item \textsl{``that the imitators differ from the bulk of their allies".} The most remarkable cases of mimicry are those where close relatives form divergent models. It is nevertheless highly possible that groups of closely related species may be similar mimics of the same model. Of course, it must always be remembered that species can look very different from their relatives because of adaptations which have nothing to do with mimicry. 
	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} This criteria, like the previous one is aimed at defining mimicry as a special adaptation. But if one of two closely related species both of which are poisonous and possess similar warning coloration, should secondarily lose its poisonous qualities, it would become a mimic and yet resemble its model in almost all its non-mimetic characters.
\end{itemize}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=5]{../tex/images/CA_rule30s}
	\caption[Cellular Automata]{Cellular Automata Rule 30.
	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
	\label{fig:cellular-automata-rule-30}
\end{figure}

>>>>

\subsubsection{Definitions of Mimicry}
The best known definition of mimicry quoted to the present day, are those given by Wallace and listed in Poulton's \textit{The color of animals, their meaning and use} \cite{poulton1890colours}. The clauses are presented in the following:

\begin{itemize}
	\item \textsl{``that the imitative species occur in the same area and occupy the same station as the imitated".}
	\item \textsl{``that the imitators are always the more defenseless".}
	\item \textsl{``that the imitators are always less numerous in individuals".}
	\item \textsl{``that the imitators differ from the bulk of their allies".}
	\item \textsl{``that the imitation, however minute, is external and visible only, never extending to internal characters or to such as do not affect the external appearance."} 
\end{itemize}

@@
